Gender Dynamics of Parliamentary Interruptions: A Detailed Analysis of Speech Disruptions in the Australian Parliament (1998-2022)

### 2025-01-15 paper/paper.qmd
edit the scripts

---
title: "Voices in Parliament: Analyzing Interruptions Across Gender in the Australian Political Landscape"
subtitle: "My subtitle if needed"
author: 
  - Hannah Yu
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/hannahyu07/Hansard_Interruptions"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| include: false
#| warning: false
#| message: false
summary(hansard_corpus)

@@

# Plot using ggplot2 with updated colors and adjusted x-axis labels
ggplot(interruption_counts, aes(x = in_gov, y = Count, fill = interject)) +
  geom_bar(stat = "identity", position = "stack") +
  facet_wrap(~ gender, scales = "free_y") +
  labs(
    title = "Interruptions Count by Government Status and Gender",
    x = "Government Status",
    y = "Count of Interruptions",
    fill = "Interruption Occurred"
  ) +
  scale_fill_manual(values = c("No" = "steelblue", "Yes" = "salmon")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 2, hjust = 0.5), # Adjust label positioning
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    legend.position = "bottom"
  )

@@

```{r}
#| include: false
#| warning: false
#| message: false
# Review entries where questions or answers are marked
question_instances <- hansard_corpus %>%
  filter(question == 1)
print(question_instances)
```

@@

# Enhanced histogram with interjection data
ggplot(hansard_corpus1 %>% filter(word_count <= 250), aes(x = word_count, fill = as.factor(interject))) +
  geom_histogram(binwidth = 25, position = "identity", alpha = 0.6) +
  labs(
    title = "Histogram of Word Counts in Speeches (Up to 250 Words)",
    x = "Word Count",
    y = "Frequency",
    fill = "Interjection Occurred"
  ) +
  scale_fill_manual(values = c("0" = "steelblue", "1" = "salmon"), labels = c("No", "Yes")) +
  theme_minimal() +
  theme(legend.position = "top") +
  theme(
   plot.title = element_text(size = 14, face = "bold", hjust = 0.5))
```
@fig-gov3 shows word counts in speeches divided into two categories: speeches where an interjection occurred and those without any interruptions. We can see that speeches without interruptions (blue bars) are more frequent across all word count ranges, especially as the number of words increases. Conversely, interrupted speeches (red bars) are less frequent and generally shorter. This trend suggests that interruptions tend to happen in shorter speeches or possibly cause speakers to shorten their remarks. This graph gives a clear visual indication of how interruptions might disrupt or influence the length of parliamentary speeches.

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-gov5
#| fig-cap: "Gender-Based Interruptions and Word Count"
# Bar plot for total speeches with real numbers on the y-axis
ggplot(summary_table, aes(x = gender, y = num_speeches, fill = factor(interject))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("steelblue", "salmon"), labels = c("No", "Yes")) +
  scale_y_continuous(labels = scales::comma) +  # Display real numbers on the y-axis
  labs(
    title = "Total Speeches by Gender and Interruption",
    x = "Gender",
    y = "Total Speeches",
    fill = "Interruption"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "top",
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

>>>>

---
title: "Gender Dynamics of Parliamentary Interruptions: A Detailed Analysis of Speech Disruptions in the Australian Parliament (1998-2022)"
subtitle: "My subtitle if needed"
author: 
  - Hannah Yu
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/hannahyu07/Hansard_Interruptions"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| warning: false
#| message: false
summary(hansard_corpus)

@@

# Plot using ggplot2 with updated colors and adjusted x-axis labels
ggplot(interruption_counts, aes(x = in_gov, y = Count, fill = interject)) +
  geom_bar(stat = "identity", position = "stack") +
  facet_wrap(~ gender, scales = "free_y") +
  labs(
    title = "Interruptions Count by Government Status and Gender",
    x = "Government Status",
    y = "Count of Interruptions",
    fill = "Interruption Occurred"
  ) +
  scale_fill_manual(values = c("No" = "steelblue", "Yes" = "salmon")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 7, angle = 0, vjust = 2, hjust = 0.5), # Adjust label positioning
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    legend.position = "bottom"
  )

@@

```{r}
#| warning: false
#| message: false
# Review entries where questions or answers are marked
question_instances <- hansard_corpus %>%
  filter(question == 1)
print(question_instances)
```

@@

# Enhanced histogram with interjection data
ggplot(hansard_corpus1 %>% filter(word_count <= 250), aes(x = word_count, fill = as.factor(interject))) +
  geom_histogram(binwidth = 25, position = "identity", alpha = 0.6) +
  labs(
    title = "Histogram of Word Counts in Speeches",
    x = "Word Count",
    y = "Frequency",
    fill = "Interjection Occurred"
  ) +
  scale_fill_manual(values = c("0" = "steelblue", "1" = "salmon"), labels = c("No", "Yes")) +
  theme_minimal() +
  theme(legend.position = "top") +
  theme(
   plot.title = element_text(size = 14, face = "bold", hjust = 0.5))
```
@fig-gov3 shows word counts in speeches divided into two categories: speeches where an interjection occurred and those without any interruptions. We can see that speeches without interruptions (blue bars) are more frequent across all word count ranges, especially as the number of words increases. Conversely, interrupted speeches (red bars) are less frequent and generally shorter. This trend suggests that interruptions tend to happen in shorter speeches or possibly cause speakers to shorten their remarks. This graph gives a clear visual indication of how interruptions might disrupt or influence the length of parliamentary speeches.

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-gov5
#| fig-cap: "Gender-Based Interruptions and Word Count"
# Bar plot for total speeches with real numbers on the y-axis
ggplot(summary_table, aes(x = gender, y = average_words, fill = factor(interject))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("steelblue", "salmon"), labels = c("No", "Yes")) +
  scale_y_continuous(labels = scales::comma) +  # Display real numbers on the y-axis
  labs(
    title = "Gender-Based Interruptions and Word Count",
    x = "Gender",
    y = "Total Speeches",
    fill = "Interruption"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "top",
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )
